\documentclass[11pt,a4paper,sans]{moderncv}

% --- ModernCV Style Setup ---
\moderncvstyle{banking}  % 'banking' style centers headers and is clean
\moderncvcolor{blue}     % Color options: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey', 'black'

% --- Character Encoding & Fonts ---
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{cmap} % Improves text copying from PDF

% --- Page Layout ---
\usepackage[scale=0.94, top=1.5cm, bottom=1.5cm]{geometry}
\setlength{\hintscolumnwidth}{3cm} % Adjusted for better spacing

% --- Packages for Columns & Lists ---
\usepackage{paracol}
\usepackage{enumitem} % For custom bullet lists
\setlist[itemize]{label=\textbullet, nosep, leftmargin=*} % Tight bullet points

% --- Personal Information ---
\name{Olivier}{Recher}
\title{Apprentice Full Stack Developer / Software Engineering Intern}
\address{Toulouse}{France}
\phone[mobile]{+33~6~19~01~36~44}
\email{recher.olivier@outlook.fr}
\homepage{www.olivier-recher.com}
\social[github]{OlivierRecher} %

% --- Document Start ---
\begin{document}

\makecvtitle

% --- Professional Summary (Full Width) ---
\vspace*{-1em} % Slight visual adjustment to pull summary up
\small{Apprentice Full Stack Developer with 4+ years of experience delivering scalable products in Symfony, Nuxt/Vue, TypeScript, PHP, and Node.js. Strong focus on translating business needs into maintainable features and optimizing performance. Looking for a Summer Internship (Available from July) to grow technical depth and cross-cultural collaboration skills.}
\vspace*{1em}

% --- Two Column Layout Start ---
\columnratio{0.25} % 32% Left, 68% Right
\setlength{\columnsep}{2em} % Gap between columns

\begin{paracol}{2}

% ---------------------------------------------------------
% LEFT COLUMN (Sidebar)
% ---------------------------------------------------------

\section{Technical Skills}
\textbf{Frontend}
\begin{itemize}
    \item Vue.js (Nuxt), React, Angular
    \item TypeScript, JavaScript
    \item Tailwind CSS, Responsive UI
\end{itemize}
\medskip

\textbf{Backend}
\begin{itemize}
    \item Symfony, PHP, Node.js
    \item REST APIs, JWT/OAuth
    \item Microservices Architecture
\end{itemize}
\medskip

\textbf{Programming \& Data}
\begin{itemize}
    \item Java, Python, C, Bash
    \item SQL (MySQL, PostgreSQL)
    \item NoSQL (MongoDB)
\end{itemize}
\medskip

\textbf{DevOps \& Tools}
\begin{itemize}
    \item Git (GitHub/GitLab)
    \item Docker, CI/CD Pipelines
    \item Linux, Vercel, Postman
\end{itemize}

\section{Languages}
\begin{itemize}
    \item \textbf{French:} Native (C2)
    \item \textbf{English:} Fluent (C1) \\ \textit{TOEIC: 940/990}
\end{itemize}

\section{Soft Skills}
\begin{itemize}
    \item Teamwork \& Collaboration
    \item Proactive Communication
    \item Critical Thinking
    \item Autonomy \& Adaptability
\end{itemize}

\section{Interests}
\begin{itemize}
    \item \textbf{Fitness:} Weight training (discipline, goal setting)
    \item \textbf{Travel:} Cultural openness
\end{itemize}

\switchcolumn

% ---------------------------------------------------------
% RIGHT COLUMN (Main Content)
% ---------------------------------------------------------

\section{Professional Experience}

\cvitem[0.75em]{}{\textbf{Apprentice Full Stack Developer} \hfill \textit{2023 -- Present} \\ \textit{Finvens} \hfill \textit{Toulouse}}
\begin{itemize}
    \item Migrated a business-critical application (200+ daily users) from legacy PHP 5 to Symfony 6 REST APIs and Nuxt 3/Vue/TypeScript frontends.
    \item Optimized data models and led feature redesigns, resulting in improved application performance and code maintainability.
    \item Collaborated closely with Product, QA, and Support teams in Agile/Scrum rituals to ensure seamless delivery.
\end{itemize}

\vspace*{0.5em}

\cvitem[0.75em]{}{\textbf{Apprentice Full Stack Developer} \hfill \textit{2022 -- 2023} \\ \textit{Sopra Steria} \hfill \textit{Toulouse}}
\begin{itemize}
    \item Designed, developed, and delivered a custom ERP used by 80+ employees across 10 distinct teams.
    \item Built web-based management tools using JavaScript, PHP, and SQL to handle schedules, meeting rooms, and leave requests.
    \item Managed the full lifecycle: requirements gathering, UI/UX design, database architecture, and end-to-end implementation.
\end{itemize}

\section{Education}

\cvitem[0.75em]{}{\textbf{M.Sc. in Engineering (Diplôme d'Ingénieur)} \hfill \textit{2024 -- 2027} \\ \textit{Ecole Nationale Supérieure des Mines d'Alès} \hfill \textit{Alès}}
\cvitem{}{Top-tier French engineering school with focus on Software Engineering.}

\vspace*{0.5em}

\cvitem[0.75em]{}{\textbf{Bachelor of Technology in Computer Science} \hfill \textit{2021 -- 2024} \\ \textit{Université Toulouse - Jean Jaurès} \hfill \textit{Toulouse}}
\cvitem{}{Specialization in Application Development.}

\section{Personal Projects}

% Using a custom format for projects to save space and look cleaner
\textbf{Portfolio Website} \hfill \textit{Nuxt, TypeScript, Tailwind}
\begin{itemize}
    \item High-performance showcase website emphasizing UI/UX and automated deployment workflows.
\end{itemize}
\medskip

\textbf{Pomodoro App} \hfill \textit{Flutter, Dart}
\begin{itemize}
    \item Mobile application featuring task management, custom timers, and push notifications.
\end{itemize}
\medskip

\textbf{Accounting Firm Website} \hfill \textit{React, Tailwind}
\begin{itemize}
    \item Developed a commercial site that improved inbound leads and SEO ranking for a local firm.
\end{itemize}
\medskip

\textbf{AI Doodle Jump} \hfill \textit{JavaScript, Neural Networks}
\begin{itemize}
    \item Implemented a genetic algorithm and neural network to create a self-learning autopilot for the game.
\end{itemize}

\textbf{Drone Delivery App} \hfill \textit{React Native, TypeScript, Node.js, MongoDB}
\begin{itemize}
    \item Built a drone delivery mobile app with secure authentication, order flows, and real-time tracking connected to a drone simulator.
\end{itemize}

\end{paracol}

\end{document}